%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[10pt,a4paper]{article} % Font size (10-12pt) and paper size (a4paper, letterpaper, legalpaper, etc)

\include{structure} % Include structure.tex which contains packages and document layout definitions

\hyphenation{Some-long-word} % Specify custom hyphenation points in words with dashes where you would like hyphenation to occur, or alternatively, don't put any dashes in a word to stop hyphenation altogether

\begin{document} 

%----------------------------------------------------------------------------------------
%	NAME AND CONTACT INFORMATION
%----------------------------------------------------------------------------------------

\maintitle{JiaYi Zhang}{May 25, 1998}  % Your name and date of birth or subtitle

\noindent\href{mailto:itzmeerkat@gmail.com}{itzmeerkat@gmail.com}\bull % Your email address
\textsmaller{+}1 669-294-6252\\ 

625 Cantrill DR \bull  Davis\bull CA  \bull United States\bull 95618 % Your address

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------



\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{University of California, Davis | GPA 3.504  }
{\textsc{Davis, CA United States}} {
	
	\headedsubsection % Job title entry for the current employer
	{Bachelor degree: Major in Computer Science}
	{2018 -- 2020}
	{\bodytext{
		Reinforcment learning for AI; Algorithms in computer vision; Machine learning from scratch\\
		Learned how to lead a team in project and how to set up procedure to approach the solution
	}
	}

}

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{De Anza college | GPA 3.70}
{\textsc{Cupertino, CA United States}} {
	
	\headedsubsection % Job title entry for the current employer
	{Associate degree: Major in Computer Science}
	{2016 -- 2018}
	{\bodytext{Assembly language, Java, C/C++\\Calculus and discrete math}
	}
	
}

%------------------------------------------------

%------------------------------------------------

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Technical specialties:}
{
	Proficient in Python/C++/Go/Matlab; Experienced in algorithm design; Farmiliar with the underlying machanism of machine learning, computer vision and artificial intellegence.\\
	Understand the priciple of operating system.\\
	Total coding experience: around 8000 lines of codes.
} 
 
%------------------------------------------------

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Leadership 2019-Present:}
{Leader of Technical Service Team in club iDEX.\\
Leader of a machine learning group project of 10 members, with various culture background.}


\spacedhrule{1.6em}{-0.4em}
\roottitle{Experience}

\headedsection
{\href{https://github.com/itzMeerkat/UCDavis-ECS171-2019Fall-Project}{Machine Learning}  }
{\textsc{Developer, Leader | Group project}} {
	\headedsubsection
	{\acr{Bay Area Bike Share number of trips prediction}}
	{Nov 2016 -- Oct 2019}
	{\bodytext{Predicting the number of trips per day in San Francisco, using LSTM model then evaluate it by comparing with FFNN and OLS.}}
}

\headedsection
{\href{https://github.com/itzMeerkat/PrintableNote}{Computer Vision}}
{\textsc{Developer, Leader | Individual project}} {

	\headedsubsection
	{\acr{Document Image Background Removal and Text Color Enhancement}}
	{May 2015 -- Apr 2016}
	{\bodytext{Take an image of a paper document as input, the program detects and removes the background even the lighting condition various across the image. Then enhance the color of foreground texts by unifying their color.}}
}

\headedsection
{\href{https://github.com/itzMeerkat/vue-ProportionalTimeline}{Web Application}}
{\textsc{Designer, Developer | Individual project}} {
	
	\headedsubsection % Job title entry for the current employer
	{\acr{Proportional Timeline}}
	{May 2018 -- Jun 2018}
	{\bodytext{A timeline web application that has a vertical axis representing the time and events will be placed based on its timestamp.}}
}

\headedsection
{\href{https://github.com/itzMeerkat/FHDAClassViewer}{Web Application}}
{\textsc{Designer, Developer | Individual project}} {
	
	\headedsubsection % Job title entry for the current employer
	{\acr{Course Search and View Website for De Anza College}}
	{Feb 2017 -- May 2017}
	{\bodytext{A better version of official class viewing website. All the data were fetched through a web crawler, from the student control panel. Since it requires access of student control panel with a valid account, I would like to keep the code private unless needed.}}
}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\roottitle{Achievement} % Top level section

\headedsection % Employer name which can include a hyperlink and location/URL on the right side of the page
{Algorithm Design Competition}
{\textsc{Beijing, China}} {
	
	\headedsubsection % Job title entry for the current employer
	{National Olympiad in Informatics}
	{2015 | Second Prize}
	{\bodytext{National Olympiad in Informatics in Provinces (NOIP) is an algorithm design competition. It requires the participants to have the skill of abstracting a problem from a realistic scene and the ability to solve the problem with the algorithm knowledge and data structure techniques.}}
	
}

%------------------------------------------------

%\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after



\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after



%----------------------------------------------------------------------------------------

\roottitle{Interests} % Top level section

\inlineheadsection % Special section that has an inline header with a 'hanging' paragraph
{Non-exhaustive and in alphabetical order:}
{Art, Chess, Historical fencing, Music and Travel.      }
 
%----------------------------------------------------------------------------------------

\end{document}