%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Cies Resume/CV
% LaTeX Template
% Version 1.1 (20/7/14)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Cies Breijs (cies@kde.nl)
% https://github.com/cies/resume with extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[10pt,a4paper]{article}
\usepackage[a4paper,margin=0.75in]{geometry}
\usepackage[english]{babel}
\hyphenation{Some-long-word}
\usepackage{resume}

\begin{document}
\sloppy
\maintitle{JiaYi Zhang}{May 25, 1998}

\nobreakvspace{0.3em}
\noindent\href{mailto:itzmeerkat@gmail.com}
{itzmeerkat\mbox{}@\mbox{}gmail.com}
\sbull
\textsmaller{+}1 669 294 6252
\sbull
\href{https://github.com/itzmeerkat}{github.com/itzmeerkat}\\625 Cantrill Dr., Davis, CA, 95618
\spacedhrule{0.9em}{-0.4em}


\roottitle{Objective}
\noindent \emph{To make exciting creation using my skills and determination.}

\spacedhrule{0.9em}{-0.4em}
\roottitle{Education}

\headedsection
{University of California, Davis | GPA 3.504  }
{\textsc{Davis, CA United States}} {
	
	\headedsubsection
	{Bachelor degree: Major in Computer Science}
	{2018 -- 2020}
	{\bodytext{
    Reinforcment learning for AI; Algorithms in computer vision; Machine learning algorithms from scratch\\
    Learned how to lead a team in project and how to set up procedure to approach the solution}
  }
}

\headedsection
{De Anza college}
{\textsc{Cupertino, CA United States}} {
	\headedsubsection
	{Associate degree: Major in Computer Science}
	{2016 -- 2018}
	{\bodytext{Assembly language, Java, C/C++\\Calculus and discrete math}
	}
}
\spacedhrule{0.9em}{-0.4em}

\roottitle{Experience}

\headedsection
  {Reinforcement Learning AI for Connect-4}
  {\textsc{Group Project}} {
  \headedsubsection
    {Artificial Intelligence}
    {01/2019 – 03/2019}
    {\bodytext{Implemente Q-Learning from scratch\\Outperform 80\% of class\\Consistently beat Monte Carlo algortithm}}
}
\vspace{0.4em}

\headedsection
  {\href{https://github.com/itzMeerkat/UCDavis-ECS171-2019Fall-Project}{BayAreaBikeShare Trip Prediction}}
  {\textsc{Group Project}} {%
  \headedsubsection
    {Machine Learning}
    {Apr \apo12 -- Oct \apo16}
    {\bodytext{Hoppinger is an open source minded \emph{full-service} internet agency.  In charge of the dev't capacity, reporting directly to managing director and co-founder Marijn Bom.  Drafted and carried out the technical company vision.  Inspired both devs and management to look beyond \acr{PHP}. Grew custom app dev't into a serious revenue segment.  Implemented continuous delivery. Created and taught several in-house courses.  Enacted testing strategy.  Recruited viciously, in part by organizing educational events.  Restructured to fixed team configurations.  Introduced DevOps (Puppet).  Helped to set up the \textit{Customer Support} and \textit{IT ops} dep'ts.  Contributed to the sales pitches for, and in charge of the software architecture for, all technically challenging projects. Involved with many company-wide process improvements.}}
}

\headedsection
  {\href{http://www.hr.nl}{Rotterdam University of Applied Sciences}}
  {\textsc{Rotterdam, The Netherlands}} {%
  \headedsubsection
    {Member of the Professional Advisory Board \textnormal{\textit{(till Sep \apo16)}} \& Guest Lecturer}
    {Sep \apo12 -- present}
    {%\bodytext{Introductory lecture on history of software development and open source for 1\textsuperscript{st} year CS students.}
    }
}

\headedsection  % sets the header for the section and includes any subsections
  {\href{http://www.intellecap.com}{Intellecap}/\href{http://istpl.in}{\acr{ISTPL}}}
  {\textsc{Mumbai, Pune \& Hyderabad, India}} {%

  \headedsubsection  % sets the header for a subsection and contains usually body text
    {\acr{IT} Consultant}
    {Nov \apo08 -- Feb \apo09}
    {\bodytext{Intellecap is a financial advisory firm serving corporates, non-profits and governments working in developing markets. Assessed their software development team and processes. Trained their devs. Architected and built several web apps; one being Mostfit an open source \acr{MIS} for \href{http://en.wikipedia.org/wiki/Microcredit}{microcredit} lenders.}}

  \headedsubsection
    {\acr{IT} \& Strategy Consultant}
    {Jan \apo10 -- Aug \apo11}
    {\bodytext{Called in to solve several technical challenges and develop growth strategies regarding Mostfit.}}

  \headedsubsection
    {CTO}
    {Oct \apo11 -- Feb \apo12}
    {\bodytext{Proudly joined the \acr{C}-family of Intellicap's software division, ISTPL, to make \href{https://github.com/Mostfit/mostfit}{Mostfit} the nr.1 software solution for micro credit lenders around the globe.  Shut down in six months due to lack of investment.}}
}

\headedsection
  {\href{http://www.zarafa.com}{Zarafa}}
  {\textsc{Delft, The Netherlands}} {%
  \headedsubsection
    {\acr{QA} \& Release Manager}
    {Dec \apo09 -- Jan \apo11}
    {\bodytext{Before 2015, when Zarafa entered in an extensive parnership with Amazon, it was probably the fastest growing open source product company in Europe, making a drop-in replacement for MS Exchange.  Reported directly to the \acr{CEO}, Brian Josef, and worked closely with the \acr{CTO}, Steve Hardy.  In charge of the 6 men strong QA dep't.  Established test automation and continuous integration.  Architected and implemented an all-integrated documentation and translation system that employed community effort.  Got sent to India to analyse and streamline their outsourced operations.}}
}

\headedsection
  {\href{http://www.dharmapublishing.com}{Dharma Publishing}}
  {\textsc{near San Francisco, \acr{USA}}} {%
  \headedsubsection
    {\acr{IT} Consultant}
    {Nov \apo09 -- Dec \apo09}
    {\bodytext{Dharma Publishing, the worlds largest Buddhist publisher, is a non-profit, all-volunteer organisation to preserve Tibetan buddhism and culture. Built their web shop, improved related processes.}}
}

\spacedhrule{-0.2em}{-0.4em}


\roottitle{Skills}

\inlineheadsection  % special section that has an inline header with a 'hanging' paragraph
  {Technical expertise:}
  {Leading and recruiting teams of software engineers.  Big fan of Agile methodologies, continuous delivery and functional programming.  Enjoys writing Ruby/\nsp Python/\nsp Java/\nsp \CPP~and Haskell.  Solid knowledge of the full web technology stack.  Able to architect \textit{and} implement distributed/\acr{HA} systems.  Strong Linux administration skills (e.g.\ Bash scripting, Apache/\acr{NGINX}, Postgres/My/No\acr{SQL}, ElasticSearch).  Well experienced with virtualization/containerization (Docker/Kubernetes, \acr{KVM}, Xen and several \acr{AWS} solutions) and DevOps (Puppet).  Emacs user.}

\vspace{0.5em}
\inlineheadsection
  {Natural languages:}
  {Dutch \emph{(mother tongue)}, English \emph{(full professional proficiency)}, German \emph{(limited working proficiency)}, French \emph{(elementary proficiency)} and Mandarin Chinese \emph{(beginner)}.}


\spacedhrule{1.6em}{-0.4em}

\roottitle{Interests}

\inlineheadsection
  {Non-exhaustive and in alphabetical order:}
  {art, Buddhism, cryptography, functional programming, Go (board game), history, music (from classical and jazz to Berlin-techno), \acr{NLP}, permaculture, philosophy, rock climbing, startups, travel, typography (e.g.\ graphic design, \LaTeX), \acr{UX}-design and vegan cuisine.}


\end{document}
